---
title: "Nitrous Acid Program in R (NAPR)"
author: "Bode Hoover"
date: "`r Sys.Date()`"
output: html_document
editor_options: 
  markdown: 
    wrap: 72
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## About me

-   Implementation of the Nitrous Acid Program in R (NAPR) for
    standardized form of calculating HONO sources and modeling [HONO]
-   Currently only working for diurnal but will add averaging option.
-   Easily use [diurnals package](https://github.com/bhoover59/diurnals)
    if needed
-   Later will make RShiny App for best UI

### Clear memory

```{r clear memory}
rm(list = ls())
```

### Get input file and functions

-   Getting functions from other scripts
-   OR put app.R shiny app in same folder!
-   **Input concentrations must be ppb**
-   You might have to adjust the working directory if functions don't
    load. They are in NAPR/R/file.R

```{r get inputs}
path <- getwd()
file <- paste(path, '/get_functions', '.R', sep = "")
source(file)
get_functions() # load files to enable functions
```

### Get input data csv

Load csv file with concentrations in ppb

```{r get input file}
df <- get_input_file()
```

### Dependencies

Install and load necessary packages

```{r load dependencies}
load_packages()
```

### Check input

They don't have to have valid data, but they must exist

```{r check input}
check_input(df)
```

### Initial parameters

Includes constants and user options Convert units to molec/cm3 from ppb

```{r initial parameters}
initial <- get_initial()
df <- convert_to_percc(df)
```

### Optional functions

Must have Rain column for filtering \* Compare options: \* Rain only = 1
\* Dry only = 0 \* All data otherwise

```{r optional}
df <- get_rain_days(df = df, compare = 0)
```

### Meteorological information

-   RH input must be **%** right now. Might update to have optional
    conversion
-   Pressure must be in **atm**. Might update to have optional
    conversion

```{r meteorological}
df <- get_met(df = df, temp_units = 'C', temp_column = 'Temp')
```

### Photolysis and TUV Model

TUV model takes a couple of minutes to run \* NCAR TUV differs
substantially from MCM & F0AM \* FIX JHONO SO IT WORKS CONSISTENTLY \*
Sometimes TUV output is weird, especially on fringes so you may need to
edit some values especially if 0 --\> infinity \* JNO2 options: \* JNO2
= 1, use JNO2 measurements \* JNO2 = 2 use TUV modeled JNO2 \* Jcorr
options: \* Jcorr = 1 calculate Jcorr by JNO2 measured/JNO2 TUV \* Jcorr
= 0 input your own column of Jcorr values \* Jcorr = 2 input JHONO
values \* Jcorr = else use ideal conditions (don't want to scale by
Jcorr), not recommended \* Calculates JHONO based on JNO2 and Jcorr

```{r TUV}
df <- TUV_hourly(df = df, date = 20220728, latitude = 45.568100, longitude = -84.682869, gAltitude = 0.2667, mAltitude = 0.26715)
df <- get_J_values(df = df, JNO2 = 1, Jcorr = 1)
```

### Run the model

```{r run model}
df_kinetics <- get_kinetics(df, initial) # get rate constants and boundary layer height
df_model <- run_model(df_kinetics, initial) # calculate HONO and unknown source
```

### Plotting

```{r plotting}
plot_HONO(df = df_model, xlab = 'Hour', ylab = '[HONO] (ppt)')
# plot_stacked_rates(df = df_model) # plot stacked loss rates with total production line
# plot_all_stacked_rates(df = df_model) # plot all individual production and loss rates stacked
plot_rates(df = df_model) # plot all individual production and loss rates stacked
plot(df_model$Hours, df_model$HONO_pss) # Plot base model
plot(df_model$Hours, df_model$HONO_model) # Plot base model
```

### Summary report

-   Print summary statistics for subset of data frame
-   Currently subsets for HONO_pss and unknown but can easily be edited

```{r summary}
report_summary(df_model)
```

### Output csv

```{r output}
output_csv(df_model, file_name = 'NAPR output') # output csv to working directory
```
